%----------------------------------------------------------------------------------------
%	SECTION TITLE
%----------------------------------------------------------------------------------------

\cvsection{Experience}

%----------------------------------------------------------------------------------------
%	SECTION CONTENT
%----------------------------------------------------------------------------------------

\begin{cventries}

%------------------------------------------------

\cventry
{Software Engineering Intern - Enterprise Security} % Job title
{Splunk Inc.} % Organization
{San Jose, CA} % Location
{May. - Aug. 2019} % Date(s)
{ % Description(s) of tasks/responsibilities
\begin{cvitems}
\item {Engineered a prediction engine to recommend analyst actions for security events using {\bf Machine Learning} models and {\bf MLTK} in {\bf Python}}
\item {Implemented a front-end interface for easy selection and execution of recommended actions in {\bf Javascript}}
\item {Added searching functionality to perform automated lookup and enrichment of user asset data}
\end{cvitems}
}

%------------------------------------------------

\cventry
{C/C++ Software Engineering} % Job title
{SSIMWAVE Inc.} % Organization
{Waterloo, ON} % Location
{Sept. - Dec. 2018} % Date(s)
{ % Description(s) of tasks/responsibilities
\begin{cvitems}
\item {Developed a CEA708 closed caption decoder for data format validation in {\bf C++}}
\item {Upgraded the video analytics pipeline to incorporate and monitor video quality metrics with increased precision}
\item {Built telecine video filters to decode interlaced video using {\bf FFmpeg} video processing libraries}
\end{cvitems}
}

%------------------------------------------------    

\cventry
{Software Developer} % Job title
{eSentire Inc.} % Organization
{Cambridge, ON} % Location
{Jan. - Apr. 2018} % Date(s)
{% Description(s) of tasks/responsibilities
\begin{cvitems}
\item {Developed and updated filters in {\bf Ruby} for {\bf Logstash} to parse audit logs from multiple sources including Dropbox, AWS, and Office 365}
% \item {Implemented system resource exporters and visualization dashboards to monitor micro-service health metrics using {\bf Prometheus}}
\item{Rewrote entire {\bf Python} testing framework to utilize a C-based {\bf Kafka} client, increasing message throughput efficiency by over 6.5x}
\end{cvitems}
}

%------------------------------------------------

\cventry
{Simulation Software Engineer} % Job title
{University of Waterloo Autonomoose} % Organization
{Waterloo, ON} % Location
{May - Aug. 2017} % Date(s)
{% Description(s) of tasks/responsibilities
\begin{cvitems}
\item {Programmed {\bf ROS Nodelets} in {\bf C++} for data transfer and virtual test monitoring}
% \item {Created a JSON based simulation scenario format to allow automated generation of virtual environments and situations for testing}
\item {Coded C++ to ROS MSG file translation and automatic function code generation in {\bf Python} to save dozens of hours of manual work}
\end{cvitems} 
}

%------------------------------------------------

\end{cventries}
